The problem and promise of scale in multilayer networks

### 2019-09-26 paper/table1.Rmd
gh doc is nice
start intro paragraph

---
output: github_document
author: Alec Robitaille, Quinn M.R. Webber, Julie Turner and Eric Vander Wal
date: "-- `r Sys.Date()`"
---

### Table 1

We determined three types of multilayer networks most relevant to spatial variables. Multilayer networks with layers defined by spatially explicit locations, interspecific interactions, and community or subpopulation structure. 
Other types of networks, such as intercontexual networks or temporal networks, are likely only to incorporate spatial variables in a hybrid multilayer network and considerations for including those variables will be explored here

In table 1, we define three types of multilayer networks that *can* incorporate spatial variables.

Multilayer networks are composed of layers, nodes, interlayer edges and intralayer edges. Layers are

@@

```{r, echo = FALSE}
library(data.table)
tab1 <- fread('table1.csv')
knitr::kable(tab1)
```

>>>>

---
output: 
#   pdf_document
# classoption: landscape
  # word_document:
  #   reference_docx: template.docx
  github_document
author: Alec Robitaille, Quinn M.R. Webber, Julie Turner and Eric Vander Wal
date: "-- `r Sys.Date()`"
---

### Table 1
In Table 1, we define three types of multilayer networks that incorporate spatial variables. Multilayer networks are composed of layers, nodes, interlayer edges and intralayer edges. Layers represent the different types of relationships, individuals or contexts of the social system. Nodes represent individual entities in the network, connected by some association or relationship with edges. Interlayer edges connect layers to other layers or individuals across layers. Intralayer edges connect individuals to other individuals within a network layer.

Depending on the type of network, interlayer edges connect individuals to themselves across different contexts or to different individuals

multilayer networks with layers defined by spatially explicit locations, interspecific interactions, and community or subpopulation structure. 
Other types of networks, such as intercontexual networks or temporal networks, are likely only to incorporate spatial variables in a hybrid multilayer network and considerations for including those variables will be explored here

An animal's social network is multifaceted and complex, though this system is often examined

@@

```{r, echo = FALSE, warning = FALSE}
# library(pander)
# panderOptions('table.alignment.default', function(df)
#     ifelse(sapply(df, is.numeric), 'right', 'left'))
# panderOptions('table.split.table', Inf)
# panderOptions('big.mark', ",")
# panderOptions('keep.trailing.zeros', TRUE)

library(data.table)
library(magrittr)
library(kableExtra)

tab1 <- fread('table1.csv')

options(knitr.table.format = "markdown")

knitr::kable(tab1[c(1:7, 9)])
```
